Reconstructing the last known movements of one of Nature's giants

### 2017-06-24 manuscript/blue-whale-ms.tex
Corrected figure names

% figure 1
\begin{figure}
  \centering
  \includegraphics[width = \linewidth]{figures/Figure-1a-raw-dC-dN-data.png}
  \label{fig1}
  \caption{One panel figure}
\end{figure}

% figure 2
\begin{figure}
  \centering
  \includegraphics[width = \linewidth]{figures/Figure-1b-migratory-model-full-map.png}
  \label{fig2}
  \caption{One panel figure}
\end{figure}

% figure 3
\begin{figure}
  \centering
  \includegraphics[width = \linewidth]{figures/Figure-1c-migratory-model-d13C.png}
  \label{fig3}
  \caption{One panel figure}
\end{figure}

@@

>>>>

% figure 1
\begin{figure}
  \centering
  \includegraphics[width = \linewidth]{figures/Figure-1-raw-dC-dN-data.png}
  \label{fig1}
  \caption{One panel figure}% Can you add these?
\end{figure}

@@

% figure 2
\begin{figure}
  \centering
  \includegraphics[width = \linewidth]{figures/Figure-2-migratory-model-full-map.png}
  \label{fig2}
  \caption{One panel figure}% Can you add these?
\end{figure}

% figure 3
\begin{figure}
  \centering
  \includegraphics[width = \linewidth]{figures/Figure-3-migratory-model-d13C.png}
  \label{fig3}
  \caption{One panel figure}% Can you add these?
\end{figure}
